Estimating Trending Topics on Twitter with Small Subsets of the Total Data

### 2015-01-12 521_project_paper.tex
Updated algorithms and analysis

Things to add:
abstract
clear definition of problem and motivation 
adapt proposal -> introduction stuff
background work: cm-sketch, hokusai (algorithm), specific twitter trending work: ? 
http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=6137387&tag=1 
(this is the closest we could find)
(to the best of our knowledge, this work has not been done before)

@@

To this structure we add another layer that combines these Count-Min sketches into a single Count-Min sketch that depreciates the value of older data.  This aggregate Count-Min sketch stores the values $\bar{M} + \sum\limits_{j=1}^{\log⁡(T)} \frac{M^j}{2^j}$ where $\bar{M}$ is the Count-Min sketch storing today's data, $M^j$ is the Count-Min sketch storing the data for the sketch with a $2^j$ resolution, and $T$ is an upper bound on the number of days stored by the data structure.  In section \ref{Correct} we will show that this aggregate Count-Min sketch weights the hashtags that occurred $i$ days ago with value approximately $\frac{1}{2i}$.

@@

\begin{algorithm}
\caption{Thread to process data input.}
\begin{algorithmic}[1]
\While {data arrives}
	\If {hashtag is in hash table}
		\State Increment the frequency stored at that entry.
		\State Update the key of the node in the Fibonacci heap.
	\Else
		\State Insert a new node into the Fibonacci heap with the appropriate key and value. 
		\State Insert the hashtag into the hash table with a pointer to this node.
 	\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Thread to discard oldest recent hashtags.}
\begin{algorithmic}[1]
\Loop
	\If {queue is not empty}
		\State Peek at end of queue.
		\If {the timestamp + $y$ minutes is before the current time}
			\State Look up the hashtag in the hash table and decrement the stored frequency.
			\If {the frequency is now 0}
				\State Delete the node in the heap pointed to by this entry in the table.
				\State Delete this entry in the hash table.
			\Else	
				\State Update the key of this node pointed to by this entry in the table to the proper value given the new frequency.
			\EndIf
		\EndIf
	\EndIf
\EndLoop
\State Make the hash table for the oldest $x$ minute interval correspond to the upcoming $x$ minute interval.

\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Updates at end of a day.}
\begin{algorithmic}[1]
\State Do all the end-of-day aggregation for the Hokusai structure as detailed in Algorithm \ref{alg1}.
\ForAll {elements in the Fibonacci heap}
	\State look up the hashtag corresponding to this node in the hash table
	\State Update the key of the node to: \[\frac{\text{frequency in last y minutes found at the table entry}}{\text{new value in Hokusai data structure}}\]
\EndFor
\end{algorithmic}
\end{algorithm}

@@

Time for actions when day ends:
Takes O(nm) amortized time to do all end of day aggregation.
Takes O(m) time to compute each key.
Takes O(1) amortized time to update each key since all keys are nondecreasing.

Thus, takes O(nm + s) amortized time + O(ms) time at the end of the day.

>>>>

Things to add:
abstract
clear definition of problem and motivation 
adapt proposal -> introduction stuff
background work: cm-sketch, hokusai (algorithm), specific twitter trending work: ? 
%http://ieeexplore.ieee.org/xpls/abs_all.jsp?arnumber=6137387&tag=1 
(this is the closest we could find)
(to the best of our knowledge, this work has not been done before)

@@

To this structure we add another layer that combines these Count-Min sketches into a single Count-Min sketch that depreciates the value of older data.  This aggregate Count-Min sketch stores the values $\bar{M} + \sum\limits_{j=0}^{\log⁡(T)} \frac{M^j}{2^j}$ where $\bar{M}$ is the Count-Min sketch storing today's data, $M^j$ is the Count-Min sketch storing the data for the sketch with a $2^j$ resolution, and $T$ is an upper bound on the number of days stored by the data structure.  In section \ref{Correct} we will show that this aggregate Count-Min sketch weights the hashtags that occurred $i$ days ago with value approximately $\frac{1}{2i}$.

@@

\begin{algorithm}
\caption{Thread to process data input.}
\begin{algorithmic}[1]
\While {data arrives}
	\If {the current day is different than that of the last hashtag seen}
		\State Do all the end-of-day aggregation for the Hokusai structure as detailed in Algorithm \ref{alg1}.
		\ForAll {elements in the Fibonacci heap}
			\State look up the hashtag corresponding to this node in the hash table
			\State Update the key of the node to: \[\frac{\text{frequency in last y minutes found at the table entry}}{\text{new value in Hokusai data structure}}\]
		\EndFor
	\EndIf
	\If {queue is not empty}
		\State Peek at end of queue.
		\If {the timestamp + $y$ minutes is before the current time}
			\State Look up the hashtag in the hash table and decrement the stored frequency.
			\If {the frequency is now 0}
				\State Delete the node in the heap pointed to by this entry in the table.
				\State Delete this entry in the hash table.
			\Else	
				\State Update the key of this node pointed to by this entry in the table to the proper value given the new frequency.
			\EndIf
		\EndIf
	\EndIf
	\If {hashtag is in hash table}
		\State Increment the frequency stored at that entry.
		\State Update the key of the node in the Fibonacci heap.
	\Else
		\State Insert a new node into the Fibonacci heap with the appropriate key and value. 
		\State Insert the hashtag into the hash table with a pointer to this node.
 	\EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

Time for actions when day ends:
Takes O(nm) amortized time to do all end of day aggregation.
Takes O(m) time to compute each key.
Takes O(log(s)) amortized time to update each key.

Thus, takes O(nm + slog(s)) amortized time + O(ms) time at the end of the day.
